Malacology: A Programmable Storage System Built on Ceph

### 2016-05-09 paper/paper.tex
sec5
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

The second service implemented on Malacology is ZLog, and a high-performance
distributed shared-log that is based on the CORFU protocol~\cite{corfu}. A
shared-log is a general, yet powerful abstraction used to build many
distributed systems. However, existing implementations that rely on consensus
algorithms such as PAXOS funnel I/O through a single point introducing a
bottleneck that restricts throughput. In contrast, the CORFU protocol is able
to achieve high throughput using a \emph{volatile} in-memory network counter
service (called a \emph{sequencer}) that distributes log positions to clients,
and may run at very high rates. Failures in CORFU are handled by a recovery
algorithm that recomputes the sequencer state using custom storage interfaces
to discover the tail of the log.

A full dexription ...

that computes the
tail of the log by contacting each storage device

Two i

The CORFU protocol handles failures using a combination of

Failures in CORFU are handled using a recovery protocol that res

The CORFU protocol is enforced using logical storage devices.

\begin{figure}[htbp]
\centering
\includegraphics{figures/overview-zlog.png}
\caption{This is ZLog.}
\end{figure}

@@

>>>>

The second service implemented on Malacology is ZLog, a high-performance
distributed shared-log that is based on the CORFU protocol~\cite{corfu}. A
shared-log is a general, yet powerful abstraction used to build many
distributed systems. However, existing implementations that rely on consensus
algorithms such as PAXOS funnel I/O through a single point introducing a
bottleneck that restricts throughput. In contrast, the CORFU protocol is able
to achieve high throughput network counter service (called a \emph{sequencer})
that avoids all persistent I/O in the common case.

While a full description of the CORFU system is beyond the scope of this
paper, we'll briefly describe the storage interface, sequencer, and recovery
protocol that form the core components of CORFU that we implement within
Malacology:

{\bf Sequencer.}
High-performance in CORFU is achived using a sequencer service that assigns
client log positions by reading from a volatile, in-memory counter which can
run at a very high throughput and at low-latency. Since the sequencer is
centralized, ensuring seiralizability in the common case is trivial.  The
primary challenge in CORFU is handling the failure of the sequencer in a way
that guarantees correctness.  Failures of the sequencer service in CORFU are
handled by a recovery algorithm that recomputes the new sequencer state using
an application-specific custom storage interface to discover the tail of the
log and invalidate stale client requests using an epoch-based protocol.

{\bf Storage Interface.} The storage interface is a critical component in the
CORFU design. Storage devices must provide a \emph{write}-once, random
\emph{read} interface for reading and writing log entries. The key to
correctness in CORFU lies with the enforcement of up-to-date epoch tags on
client requests; requests tagged with out-of-date epoch values are rejected,
and clients are expected to request a new tail from the sequencer after
refreshing state from an auxillary service. This mechanism forms the basis for
sequencer recovery.

{\bf Sequencer Recovery.}
In order to repopulate the cached tail value during recovery of a sequencer,
the maximum position in the log must be obtained. To do this, the storage
interface exposes an additional \emph{seal} method that atomically installs a
new epoch value and returns the maximum log position that has been written.
Since the recovery protocol does not inform clients of a new epoch value until
the end of the process, the validity of the tail can be guaranteed despite the
iterative process of contacting storage devices.  Recovery of the sequencer
process itself may be handled in many ways, such as leader election using an
auxillary service such as PAXOS.

\subsubsection{Log Management}

@@

%\begin{figure}[htbp]
%\centering
%\includegraphics{figures/overview-zlog.png}
%\caption{This is ZLog.}
%\end{figure}

\subsection{Interface Installation}
